Effective parameters of ferroelectric dielectric mixtures

### 2019-06-10 poster/main_poster.tex
poster and corrections

%%%%%%%%%%%  ABSTRACT %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{textblock*}{79.5cm}(2.5cm,16.2cm)
% \textcolor{fresneldarkblue}{\rule{\columnwidth}{5pt}}\\
%  {\color{fresneldarkblue}\bfseries Abstract:}
{\color{white}{ \blackfont  \bfseries \large \uppercase{Abstract}\\} \vspace{0.5em} 
  \large \itshape
  We investigate the homogenized parameters of ferroelectric-dielectric composites under a static electric field. A numerical model that takes into account the coupling
  between the electrostatic problem and the electric field dependent permittivity of the
  ferroelectric material is used. Metamaterials consisting of periodic and random arrays of rods
  are considered for transverse electric polarization case
  and we study their effective permittivity, losses, electrically induced anisotropy
  and tunability by a two scale convergence homogenization method.}
\end{textblock*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%% Left column  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% 
%%%%%%%%%%%  BOX1 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{textblock*}{38.5cm}(2.5cm,29cm)

@@

\begin{columns}[t,totalwidth=\columnwidth]
\begin{column}{.55\columnwidth}

  Ferroelectric materials play a crucial role in reconfigurable
  microwave devices, with typical applications including antenna beam steering,
  phase shifters, tunable power splitters, filters, voltage controlled oscillators and
  matching networks \cite{tagantsev_ferroelectric_2018}.

\mysubtitle{Ferroelectric permittivity}

\begin{equation}
 \epsf(E) = \left[\frac{\partial^2 F (P, E)}{\partial P^2} \right]^{-1} = \frac{\epsf(0)}{1 + \alpha P_0^2 + \beta P_0^4},
 \label{eq_epsf}
\end{equation}

\mysubtitle{Normalization of modes}

\mysubtitle{Expansion of the coupled modes}

\end{column}
\begin{column}{.40\columnwidth}
% \vspace*{2cm}
% \begin{figure}
% \centering
% \input{./figures/schemafig1}
%  \end{figure}

@@

\end{posterblock}
\end{textblock*}
% 
% % 
% %%%%%%%%%%%%% BOX 3 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% \begin{textblock*}{38.5cm}(2.5cm,72cm)
% \begin{posterblock}{Results}{benchcolor1}
%  \mysubtitle{Dielectric rod dimmer}\vspace{-1.5cm}
% 
% \vspace*{0.7cm}
% TE polarization $\B E=E_z\B z$, $\varepsilon_a=\varepsilon_b=10-0.01\ic$, $\varepsilon_h=1$, 
% $\mu_a=\mu_b=\mu_h=1$, $L_x=10^{-2}\,$m, $L_y=3L_x$, gap $d$, $\omega_0=2\pi c/L_y$.
% 
% \begin{columns}[b,totalwidth=\columnwidth]
% \begin{column}{.49\columnwidth}
%  \begin{figure}
%  \centering
%  \includegraphics[width=\columnwidth]{./figures/figd2}
%  \caption{Real (top) and imaginary (bottom) parts of the eigenfrequencies for the first four 
%  coupled modes as a function of normalized gap $d/L_x$. Circles: coupled modes (full wave direct computation), 
%  solid lines: 1 mode coupling model.}
% \end{figure}
% \end{column}
% \begin{column}{.49\columnwidth}
% \vspace*{1cm}\\
% \begin{figure}
%  \centering
%  \includegraphics[width=0.5\columnwidth]{./figures/singlerod1}
%   \includegraphics[width=0.5\columnwidth]{./figures/singlerod2}
%  \caption{Eigenfield $\re(E_z)$ for the modes of the isolated rod.}
% \end{figure}
% \begin{figure}
%  \centering
%  \includegraphics[width=0.5\columnwidth]{./figures/test1}
%   \includegraphics[width=0.5\columnwidth]{./figures/test2}\\
%    \includegraphics[width=0.5\columnwidth]{./figures/test3}
%   \includegraphics[width=0.5\columnwidth]{./figures/test4}\\
%  \caption{Eigenfield $\re(E_z)$ for the coupled modes, $d/L_x=2.1$.}
% \end{figure}
% 
% \end{column}
% \end{columns}
% \vspace*{1cm}
% Very good agreement is obtained with this simple one mode model. \\
% The study of the phase difference between the coefficients $A_i$ and $B_i$ 
% indicates an in-phase (resp. out of phase) hybridization mechanism 
% for modes $C1$ and $C3$ (resp. $C2$ and $C4$).
% 
% \end{posterblock}
% 
% \end{textblock*}
% % 
% % 
% % % 
% % % %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% % % 
% % %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% % %%%%%%%%%%% Right column  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% % %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% % 
% % %%%%%%%%%%%%%%%%%%  BOX %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% % 
% \begin{textblock*}{38.5cm}(43.5cm,29cm)
% \begin{posterblock}{Results}{benchcolor1}
% 
%  \mysubtitle{Breaking the symmetry}
% Shift $e$ along $y$, $d/L_x=1$.
% 
% \begin{columns}[b,totalwidth=\columnwidth]
% \begin{column}{.49\columnwidth}
% 
% \begin{figure}
% \includegraphics[width=\columnwidth]{./figures/figfne}
%  \caption{Real (top) and imaginary (bottom) parts of the eigenfrequencies for the first four 
%  coupled modes as a function of normalized shift $e/L_y$. Circles: coupled modes (full wave direct computation), 
%  solid lines: 4 modes coupling model.}
%  \end{figure}
% \end{column}
% \begin{column}{.49\columnwidth}
% 
%  \begin{figure}
%   \includegraphics[width=\columnwidth]{./figures/AN}\\
%   \includegraphics[width=0.5\columnwidth]{./figures/etest3}
%   \includegraphics[width=0.5\columnwidth]{./figures/etest4}
%  \caption{Top: norm of coupling coefficient $A$ as a function of 
%  normalized shift $e/L_y$. Bottom: coupled modes for $e/L_y=0.2$.}
%  \end{figure}
% \end{column}
% \end{columns}
% 
% \vspace*{1cm}
% Good agreement is obtained between full wave calculations and our model. \\
% The shift breaks the symmetry of the coupling mechanism, as revealed by 
% the study of the coefficients $A_i$ and $B_i$. For modes $C3$ and $C4$, 
% both modes $A1$ and $A2$ are significantly coupled when $e\neq0$.
% \end{posterblock}
% \end{textblock*}
% % 
% % 
% %%%%%%%%%%%%%%%%%%  BOX %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% \begin{textblock*}{38.5cm}(43.5cm,68.3cm)
% \begin{posterblock}{Conclusion and outlook}{benchcolor1}
% We developped a model for the coupling of quasi-normal modes in meta-molecules, allowing 
% for a fast computation of coupled complex eigenfrequencies and QNMs. The validity of 
% our approach has been illustrated with an example of a dielectric nanorod dimmer. It 
% is found that shifting one of the resonator perpendicular to the dimmer axis induce a 
% symmetry breaking of the coupling mechanism.\\
% Future research directions includes:
% \begin{itemize}
%    \item model for TM polarization
%    \item include magnetic material	
%    \item include dispersion \cite{QNM3}
%    \item more than two coupled resonators
%     \item 3D model
%   \end{itemize}
% 
% \end{posterblock}
% 
% \end{textblock*}
% % % 
% % % 
% %%%%%%%%%%%%%%%%%%%%%  Reference box %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
\begin{textblock*}{38.5cm}(43.5cm,86.cm)
\myblocktitle{References}{fresnelgreenblue}
\color{fresnelblack}
\printbibliography
\end{textblock*}

%%%%%%%%%%%%%%%%%%%%%  Acknowledgments box %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{textblock*}{38.5cm}(43.5cm,105.cm)
\myblocktitle{Acknowledgments}{fresnelgreenblue}
\color{fresnelblack}
This work was funded by the Engineering and Physical
Sciences Research Council (EPSRC), UK under a
Programme Grant (EP/I034548/1) ‘‘The Quest for
Ultimate Electromagnetics using Spatial Transformations
(QUEST).’’
\end{textblock*}
%

@@

{\hfill\semiboldfont \bfseries \color{fresnelorange} \Large CONTACT \& LINKS}\\
\vspace*{0.5em}
\color{white}
\hfill Corresponding author: Benjamin Vial |~\textcolor{fresnelorange}{\href{mailto:b.vial@qmul.ac.uk}{\faEnvelope~b.vial@qmul.ac.uk}}\\
\hfill QUEST |~\textcolor{fresnelorange}{\href{http://www.quest-spatial-transformation.org}{\faExternalLink~www.quest-spatial-transformation.org}}\\
\hfill Antennas \& Electromagnetics Research Group |~\textcolor{fresnelorange}{\href{http://antennas.eecs.qmul.ac.uk}{\faExternalLink~antennas.eecs.qmul.ac.uk}}

@@

\begin{textblock*}{6cm}(10cm,114.5cm)
 \includegraphics[width=\columnwidth]{./logos/logo_qmul.png}
\end{textblock*}
% 
% \begin{textblock*}{10.8cm}(17.6cm,114cm)
%  \includegraphics[width=\columnwidth]{./logos/logo_qmul.png}%{logo_black.png}
% \end{textblock*}
% 
% \begin{textblock*}{8cm}(30.cm,114cm)
%  \includegraphics[width=\columnwidth]{./logos/logo_exeter.png}
% \end{textblock*}
% 
% \begin{textblock*}{8.7cm}(39.5cm,114cm)
%  \includegraphics[width=\columnwidth]{./logos/logo_oxford.png}
% \end{textblock*}

>>>>

%%%%%%%%%%%  ABSTRACT %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{textblock*}{79.5cm}(2.5cm,12.2cm)
% \textcolor{fresneldarkblue}{\rule{\columnwidth}{5pt}}\\
%  {\color{fresneldarkblue}\bfseries Abstract:}
{\color{white}{ \blackfont  \bfseries \large \uppercase{Abstract}\\} \vspace{0.5em}
  \large \itshape
  \begin{columns}[t,totalwidth=\columnwidth]

  \begin{column}{.48\columnwidth}
    We investigate the homogenized parameters of ferroelectric-dielectric composites under a static electric field. A numerical model that takes into account the coupling
    between the electrostatic problem and the electric field dependent permittivity of the
    ferroelectric material is used.
  \end{column}

  \begin{column}{.48\columnwidth}
    Metamaterials consisting of periodic and random arrays of rods
      are considered for transverse electric polarization case
      and we study their effective permittivity, losses, electrically induced anisotropy
      and tunability by a two scale convergence homogenization method.
  \end{column}

\end{columns}

}
\end{textblock*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%% Left column  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%%%%%%%%%%%  BOX1 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%  BOX1 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{textblock*}{38.5cm}(2.5cm,22.5cm)
  \begin{posterblock}{Context}{benchcolor1}
    Ferroelectric materials play a crucial role in reconfigurable
    microwave devices, with typical applications including antenna beam steering,
    phase shifters, tunable power splitters, filters, voltage controlled oscillators and
    matching networks \cite{tagantsev_ferroelectric_2018}, and the key requirements are large tunability and low losses.
     These materials have high permittivity values even at microwave frequencies, which can be an issue in some practical
     applications. Thus it has been considered to mix ferroelectrics to low-index and
     low-loss non-tunable dielectrics in order to reduce both permittivity values and losses, or to
     use porous ceramics \cite{sherman_ferroelectric-dielectric_2006,padurariu_tailoring_2012}.

\end{posterblock}
\end{textblock*}

\begin{textblock*}{38.5cm}(2.5cm,35cm)

@@

\begin{columns}[t,totalwidth=\columnwidth]
\begin{column}{.5\columnwidth}

\mysubtitle{Ferroelectric permittivity}
Landau potential
given by $F(P,E) = F_0 +  a P^2/2 + b P^4/4 + cP^6/6 - EP$, where $E$ is
the applied electric field and $P$ is the polarization \cite{landau_electrodynamics_2013, zhou_dielectric_2008}
\begin{equation}
 \epsf(E) = \left[\frac{\partial^2 F (P, E)}{\partial P^2} \right]^{-1} = \frac{\epsf(0)}{1 + \alpha P_0^2 + \beta P_0^4},
 \label{eq_epsf}
\end{equation}
Anisotropy
\begin{equation}
 \epsftens (\B E) =
 \left(
 \begin{matrix}
   \epsf_{xx}(E_x) & 0               & 0 \cr
   0               & \epsf_{yy}(E_y) & 0 \cr
   0               & 0               & \epsf_{zz}(E_z) \cr

  \end{matrix}
 \right)
 \label{eq_epsftens}
\end{equation}

\mysubtitle{Electrostatic model}
Gauss' law for the potential $V$:
\begin{equation}
 \div (\epstens \grad V) = 0
 \label{eq_elstat}
\end{equation}

\end{column}
\begin{column}{.45\columnwidth}
% \vspace*{2cm}
\begin{figure}[!t]
 \centering
 \includegraphics[width=1.\columnwidth]{epsilon_fit}
 \caption{Variation of the ferroelectric permittivity as a function of the
  applied electric field.\vspace*{0.4em}
  \begin{tabular}{llll}
   case        & $\epsf(0)$ & $\alpha$ ($\rm \mu m^2/V^2$) & $\beta$ ($\rm \mu m^4/V^4$) \\ \hline
   static      & 3050       & 0.120                        & 0.024                       \\
   $f=3.8$ GHz & 165        & 0.240                        & 0.079                       \\
  \end{tabular}
  }
 \label{fig1}
\end{figure}

\mysubtitle{Coupled problem}

The electric field $\B E=-\grad V$ derived from the
solution of \equ{eq_elstat} depends on the permittivity distribution, which
itself depends on the electric field through \equ{eq_epsf}.

@@

\begin{columns}[t,totalwidth=\columnwidth]

\begin{column}{.64\columnwidth}
  \mysubtitle{Homogenization}
  Two scale convergence homogenization \cite{allaire_homogenization_1992, guenneau_homogenization_2000}, TE case:
  solutions $\psi_j$ of two annex problems
  % $\mathcal P_j$, $j=\{1, 2\}$:
  \begin{equation}
   \div \left[ \xitens \grad(\psi_j + r_j) \right] = 0,
   \label{eq_hom_annex}
  \end{equation}
  where $\B r = (x, y)^{\rm T}$ and $\xitens=\epstens^{\rm T}/ {\rm det }(\epstens)$.
  The homogenized tensor $\xihom$ is obtained with:
  \begin{equation}
   \xihom = \langle \xitens \rangle + \B \phi,
   \label{eq_hom}
  \end{equation}
  where $\langle . \rangle$ denotes the mean value over the unit cell.
  Correction terms $\B \phi_{ij} = \langle \xitens \grad \psi_i \rangle_j$.\\
\end{column}

\begin{column}{.3\columnwidth}

  \begin{figure}[!t]
   \centering
   \includegraphics[width=1.\columnwidth]{unit_cell}
   \caption{Periodic unit cell}
   \label{fig_cell}
  \end{figure}

  Effective permittivity tensor: $\epshom=\xihom^{\rm T}/ {\rm det }(\xihom)$.

\mysubtitle{Open source numerical implementation}
Equations~(\ref{eq_elstat}) and (\ref{eq_hom_annex}) are solved with a Finite Element
Method using the freewares Gmsh \cite{geuzaine_gmsh:_2009} and GetDP \cite{dular_general_1998} driven by a Python package.

\end{posterblock}
\end{textblock*}
%
% %
% %%%%%%%%%%%%% BOX 3 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\begin{textblock*}{38.5cm}(2.5cm,80cm)
\begin{posterblock}{Results}{benchcolor1}
 \mysubtitle{Periodic case}
 \begin{figure}[!t]
   \centering
   \includegraphics[width=0.9\textwidth]{convergence_per}
   \caption{Convergence of the coupled problem.
    Real part (a) and loss tangent (b) of the components of the homogenized
    permittivity tensor as a function of iteration step $i$. The distribution of
    the normalized electric field (colour map: magnitude in logarithmic scale,
    lines: equipotential contours) and of the
    $xx$ component of the permittivity tensor are shown for $i=1$
    (c and d) and $i=12$ (e and f).
   }
   \label{conv2D}
 \end{figure}
\end{posterblock}

\end{textblock*}
% %
% %
% % %
% % % %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% % %
% % %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% % %%%%%%%%%%% Right column  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% % %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %
% % %%%%%%%%%%%%%%%%%%  BOX %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %
\begin{textblock*}{38.5cm}(43.5cm,22.5cm)
\begin{posterblock}{Results}{benchcolor1}
  \vspace*{-0.7em}
   \mysubtitle{Effective parameters}
Tunability $n = \varepsilon_{xx}(0)/\varepsilon_{xx}(E)$, anisotropy factor
$a = \varepsilon_{xx}(E)/\varepsilon_{yy}(E)$

\begin{figure}[!t]
 \centering
 \includegraphics[width=0.9\textwidth]{effective_params_per}
 \caption{Effective parameters of the 2D metamaterials as a function of the
  applied electric field for various filling fraction of dielectric.
  (a): normalized permittivity, (b): normalized loss tangent, (c): normalized tunability and
  (d): anisotropy factor. The solid lines correspond to the coupled model and
  the dashed lines to the uncoupled model. Values are normalized with respect to the bulk properties.}
 \label{eff_par_2D_TM}
\end{figure}

 \mysubtitle{Pseudo-random case}
   \vspace*{-0.7em}
 \begin{figure}[!t]
  \centering
  \includegraphics[width=0.9\textwidth]{rand}
  \includegraphics[width=0.9\textwidth]{effpar_rand_cpl}
  \caption{Effective parameters of the pseudo-random composites as a function of the
   applied electric field for various filling fraction of dielectric, when the
   coupling is taken into account.
   (a): normalized permittivity, (b): normalized loss tangent, (c): normalized tunability and
   (d): anisotropy factor. The solid lines represent the average values
   over the 21 samples and the lighter error bands show a confidence interval corresponding to
   the standard deviation.}
  \label{eff_par_2Drand_TM}
 \end{figure}
\end{posterblock}

\end{textblock*}
% % %
% % %
% %%%%%%%%%%%%%%%%%%%%%  Reference box %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\begin{textblock*}{38.5cm}(43.5cm,85.1cm)
\myblocktitle{References}{fresnelgreenblue}
\color{fresnelblack}
\printbibliography
\end{textblock*}

%%%%%%%%%%%%%%%%%%%%%  Acknowledgments box %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{textblock*}{38.5cm}(43.5cm,105.cm)
\myblocktitle{Acknowledgments}{fresnelgreenblue}
\color{fresnelblack}
This work was funded by the Engineering and Physical Sciences Research
Council (EPSRC), UK, under a grant (EP/P005578/1) 'Adaptive Tools for
Electromagnetics and Materials Modelling to Bridge the Gap between
Design and Manufacturing (AOTOMAT)'
\end{textblock*}
%

@@

{\hfill\semiboldfont \bfseries \color{fresnelorange} \Large CONTACT \& LINKS}\\
\vspace*{0.5em}
\color{white}
\hfill Corresponding author: Benjamin Vial |~\textcolor{fresnelorange}{\href{mailto:b.vial@qmul.ac.uk}{\faEnvelope~b.vial@qmul.ac.uk}}
|~\textcolor{fresnelorange}{\href{http://bvial.info}{\faExternalLink~bvial.info}}\\
\hfill Github |~\textcolor{fresnelorange}{\href{https://github.com/benvial/ferromtm}{\faGithub~github.com/benvial/ferromtm}}\\
\hfill Antennas \& Electromagnetics Research Group |~\textcolor{fresnelorange}{\href{http://antennas.eecs.qmul.ac.uk}{\faExternalLink~antennas.eecs.qmul.ac.uk}}

@@

\begin{textblock*}{11cm}(10cm,114cm)
 \includegraphics[width=\columnwidth]{./logos/logo_qmul.png}
\end{textblock*}

\begin{textblock*}{5.5cm}(42.9cm,112.7cm)
 \includegraphics[width=\columnwidth]{./figs/qrcode.png}
\end{textblock*}

%
% \begin{textblock*}{10.8cm}(17.6cm,114cm)
%  \includegraphics[width=\columnwidth]{./logos/logo_qmul.png}%{logo_black.png}
% \end{textblock*}
%
% \begin{textblock*}{8cm}(30.cm,114cm)
%  \includegraphics[width=\columnwidth]{./logos/logo_exeter.png}
% \end{textblock*}
%
% \begin{textblock*}{8.7cm}(39.5cm,114cm)
%  \includegraphics[width=\columnwidth]{./logos/logo_oxford.png}
% \end{textblock*}
